---
title: "Schedule"
description: "Schedule"
menu: "main"
weight: 2
editor_options: 
  chunk_output_type: console
---


```{r schedule-setup, echo=FALSE, warning=FALSE, message=FALSE}
# Using the FullCalendar JavaScript library: https://fullcalendar.io

source('../../../R/createICS.R')
library(readxl)
library(lubridate)
library(configr)

options(knitr.kable.NA = '')

palette <- c('#8dd3c7','#ffffb3','#bebada','#fb8072','#80b1d3','#fdb462',
			 '#b3de69','#fccde5','#d9d9d9','#bc80bd','#ccebc5','#ffed6f')

lastModified <- format(file.info('../../../Schedule.xlsx')[1,]$mtime, '%B %d, %Y %I:%M%p')

meetups <- read_excel('../../../Schedule.xlsx', sheet = 'Meetups')
meetups$day <- as.Date(meetups$Date)
meetups$label <- paste0('Meetup ', meetups$StartTime, '\n', meetups$Topic)
# meetups$label <- meetups$Topic
meetups$color <- '#4A235A'
meetups$fill <- NA

# officeHours <- read_excel('../../../Schedule.xlsx', sheet = 'Office_Hours')
# officeHours$day <- as.Date(officeHours$Date)
# officeHours$label <- paste0('Office Hours\n', officeHours$StartTime, '')
# officeHours$color <- '#145A32'
# officeHours$fill <- NA
# 
# schedule <- rbind(meetups[,c('day', 'label', 'color', 'fill')],
# 				  officeHours[,c('day', 'label', 'color', 'fill')])

schedule <- meetups[,c('day', 'label', 'color', 'fill')]
					
topics <- read_excel('../../../Schedule.xlsx', sheet = 'Schedule')
topics$Start <- as.Date(topics$Start)
topics$End <- as.Date(topics$End)
for(i in 1:nrow(topics)) {
	schedule <- rbind(schedule, data.frame(
		day = topics[i,]$Start,
		label = paste0(topics[i,]$Topic, '\n\n\n'),
		color = '#000000',
		fill = palette[i]
	))
	dates <- seq(topics[i,]$Start, topics[i,]$End, by = 'day')[-1]
	for(j in seq_along(dates)) {
		schedule <- rbind(schedule, data.frame(
			day = dates[j],
			label = NA,
			color = NA,
			fill = palette[i]
		))
	}
}

start_day <- lubridate::floor_date(min(c(meetups$day, topics$Start)), "month")
end_day <- lubridate::ceiling_date(max(c(meetups$day, topics$End)), "month") - 1
```

*Note: Schedule is subject to change. Last updated `r lastModified`.*

```{r createICS, echo=FALSE, results='hide', warning=FALSE,error=FALSE,message=FALSE}
config <- read.config('../../config.toml')
outDir <- config$publishDir
meetups$starttime <- parse_date_time(paste0(as.character(meetups$Date), ' ', meetups$StartTime),
							    orders = "%Y-%m-%d %H:%M %p", tz = "America/New_York")
meetups$endtime <- parse_date_time(paste0(as.character(meetups$Date), ' ', meetups$EndTime),
								   orders = "%Y-%m-%d %H:%M %p", tz = "America/New_York")
meetups$location <- 'Zoom'
meetups$summary <- meetups$Topic
meetups$description <- ''

ics.file <- paste0('../../', outDir, '/Course_Calendar.ics')
createICS(meetups) %>% write(file = ics.file)
```


[CUNY SPS Academic Calendar](https://sps.cuny.edu/academics/academic-calendar)

```{r, echo=FALSE, results='hide'}
initialDate <- Sys.Date()
if(Sys.Date() < start_day) {
	initialDate <- start_day
} else if(Sys.Date() > end_day) {
	initialDate <- end_day
}
```

<script>

  document.addEventListener('DOMContentLoaded', function() {
    var calendarEl = document.getElementById('calendar');

    var calendar = new FullCalendar.Calendar(calendarEl, {
      initialDate: '`r initialDate`',
      initialView: 'dayGridMonth',
      headerToolbar: {
        left: 'prev,next today',
        center: 'title',
        right: 'dayGridMonth,timeGridWeek,timeGridDay,listWeek'
      },
      height: 'auto',
      navLinks: true, // can click day/week names to navigate views
      editable: true,
      selectable: true,
      selectMirror: true,
      nowIndicator: true,
      events: [
 ```{r, echo=FALSE, results = 'asis', warning=FALSE, message=FALSE, error=FALSE}
cat(paste0(c(
	paste0('{ title: "', topics$Topic, '",\n', 
	       ifelse(is.na(topics$Link), '', paste0('  url: "', topics$Link, '",\n')),
		   "  start: '", as.Date(topics$Start), "',\n",
		   "  end: '", (as.Date(topics$End)+1), "' }"),
		paste0("{ title: '", meetups$Topic, "',\n", 
	       ifelse(is.na(meetups$Link), '', paste0('  url: "', meetups$Link, '",\n')),
		   "  start: '", format(meetups$starttime, '%Y-%m-%dT%H:%M:%S'), "',\n",
		   "  end: '", format(meetups$endtime, '%Y-%m-%dT%H:%M:%S'), "' }")
	), collapse = ',\n '))
```
      ]
    });

    calendar.render();
  });

</script>

<div id='calendar'></div>


```{r printTopics, eval = FALSE, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
# This will create a table of the schedule. Set eval=TRUE to include.
topics$Start <- format(topics$Start, format = '%A, %B %d, %Y')
topics$End <- format(topics$End, format = '%A, %B %d, %Y')
knitr::kable(topics)
```

[Click here to import the course calendar into your calendar application](/Course_Calendar.ics)

